% mainfile: ../../../../master.tex

Since Tómas arrived late in Grindavík, I arrived late at work. I quickly prepare my slides for the meeting.

\subsection{MIME meeting}
% The part of the label after the colon must match the file name. Otherwise,
% conditional compilation based on task labels does NOT work.
\label{task:20180122_cj0}
\tags{meet,mime}
\authors{cj}
%\files{}
\persons{Kristinn Guðmundsson, Viggó Þór Marteinsson, René Groben, Anouk Lyver, Mia Cerfonteyn, Clara Jégousse} % Here, you can write the persons who attented the meeting

\subsubsection{Work carried out since last meeting}
% Here you can write what you have been doing since the last supervisor meeting
\begin{itemize}
    \item[-] Simultaneous extraction of DNA and RNA from culture samples.
    \item[-] Reverse transcription of extracted RNA.
    \item[-] Amplification by PCR of extracted DNA (or cDNA obtained by reverse transcription).
\end{itemize}

\subsubsection{Current work}
% Here you can write what you are doing right now
\begin{itemize}
    \item[-] Trouble shooting ... because after three attempts to extract DNA and RNA, I was never able to obtain RNA.
    \item[-] Stock inventory.
\end{itemize}

\subsubsection{Needed input}
% Here you can write which input you need and what you would like to discuss
\begin{itemize}
    \item[-] Proceed order to Medor?
    \item[-] How to obtain RNA and DNA from the same samples?
    \comment{The main suggestion I received was to split my samples (I guess my lysis) in two, and to perform the DNA and RNA extraction separately.}
    \item[-] Test MasterPure\texttrademark~ DNA Purification Kit?
    \comment{Using the Matis report by Eyo as supporting document, and  because there was no other written reports advocating for PCI isolation, Viggó accepted that one of us tries the MasterPure\texttrademark~ DNA Purification Kit by Epicentre.}
    \item[-] Pricing for HiSeq?
    \comment{According to Viggó, it is too early to worry about the price of HiSeq. He also said that it could be possible to get the samples sequenced at DeCODE for free.}
    \item[-] Winter Survey
    \comment{From the 7th February to early March. Anouk Lyver will be going. She will follow the sampling plan that was used in August. She might get a chance to get off the ship one week earlier if someone can collect the water on SB line.}
\end{itemize}


