% mainfile: ../../../../master.tex
\subsection{Extraction of total DNA and RNA from marine samples}
% The part of the label after the colon must match the file name. Otherwise,
% conditional compilation based on task labels does NOT work.
\label{task:20180104_cj1}
\tags{dna,rna,lab,exp,extr}
\authors{cj}
%\files{}
%\persons{}

I continue the nucleic acid extraction I started yesterday. The extracted RNA incubated in glycogen and isopropanol overnight at -20\degree C. The extracted DNA incubated with glycogen and 96\% ethanol overnight at -20\degree C. 
\sidenote{In reality, the samples were incubated longer than overnight because of the extra centrifugation times (cf. further steps).}

\subsubsection{Washing and resuspension of nucleic acids}

\begin{enumerate}
\item Pellet nucleic acids from previous steps by centrifugation for 30 min at maximum speed at 4\degree C.
\comment{After the first centrifugation, I can already see a pellet which for both the RNA and the DNA. I believe the glycogen helps to visualise the pellet, I also think there will be a lot of contaminents that were precipitated with the nucleic acids.}
\item Discard carefully supernatent.
\item Repeat previous steps until all RNA and RNA are respectively combined into one single 2mL-Eppendorf tube.
\comment{I must repeat the centrifugation a lot of times, because I ended up with a lot of ethanol.}
\end{enumerate}

At the end of the day, I was able to concentrate only two out six Falcon tubes into one 2mL-Eppendorf tube. I will continue tomorrow.
