% mainfile: ../../../../master.tex
\subsection{Extraction and purification of genomic DNA and total RNA from Sterivex\texttrademark~ filter with modified AllPrep\cR method}
% The part of the label after the colon must match the file name. Otherwise,
% conditional compilation based on task labels does NOT work.
\label{task:20180320_cj2}
\tags{lab,extr,dna,rna,svx}
\authors{cj}
%\files{}
%\persons{}

\subsubsection{Introduction}

AllPrep\cR DNA/RNA Kits allows the simultaneous purification of genomic DNA and total RNA from the same cell or tissue sample.

This is the final test for me before I extract my samples for \gls{sip} or metagenomics/metatranscriptomics. 

I found in the -80\degree freezer, I found a lost Sterivex\texttrademark~ filter with no label whatsoever. So I decided to use this Sterivex\texttrademark~ to make sure I can perform the extraction starting with a filter. 

\subsubsection{Sample disruption and homogenisation of cells}

\begin{enumerate}
\item Add 600~\uL of Buffer RLT in the Sterivex\texttrademark~ filter.
\item Vortex for 10 seconds.
\comment{Lysate is green-brown, and filter looks clean and white.}
\item Withdraw lysate using a 2mL serynge and transfer into a clean 2mL-Eppendorf tube.
\item Add approx. 0.2 mg of beads. \sidenote{Mia prepared them, I must check the diameters of the beads.}
\item Disrupt MixerMill MM400 by Retsch using the program P9 (300 Hz) for 10 seconds three times and immerse tube icy water for 30 sec after each round.\sidenote{Icy water allows more surface to be in contact and therefore a more efficient cooling effect compared to ice.}
\item Centrifuge the lysate for 3 min at maximum speed (20 000 x g) at 4\degree C.
\item Transfer carefully the supernatent to an AllPrep\cR DNA spin column placed in a 2~mL collection tube.
\item Close the lid.
\item Centrifuge for 30 sec. at 8000 x g.
\item Use the flow-through for RNA purification: proceed to Total RNA purification.
\item Place the AllPrep\cR DNA spin column in a new 2~mL collection tube and keep at room temperature.
\end{enumerate}

% \subsubsection{Total RNA purification}

\begin{enumerate}
\item Add 1 vol. of 70\% ethanol to the flow-through collected previously. \comment{Here, one volume is 600~\uL}
\item Mix well by pipetting.
\item Transfer up to 700~uL of the sample to an RNeasy spin column placed in a 2~mL collection tube.
\item Centrifuge for 15 sec. at 8000 x g at 4\degree C.
\item Discard the flow-through.
\item I repeat the three previous steps with the remaining volume of sample to make sure the column is saturated in RNA.
\item Add 700~\uL of Buffer RW1 to the RNeasy spin column.
\item Close the lid.
\item Centrifuge for 15 sec. at 8000 x g at 4\degree C.
\item Discard the flow-thought.
\item Add 500~\uL of Buffer RPE to the RNeasy spin column.
\item Close the lid.
\item Centrifuge for 15 sec. at 8000 x g at 4\degree C.
\item Discard the flow-thought.
\item Add 500~\uL of Buffer RPE to the RNeasy spin column.
\item Close the lid.
\item Centrifuge for 2 min at maximum speed at 4\degree C.
\item Discard the flow-thought.
\comment{At this step, I could have performed the optional step to dry the column by centrifuging at maximum speed for one min.}
\item Place the RNeasy spin column in a new 1.5~mL collection tube.
\item Add 50~\uL of RNase-free water directly to the spin column membrane. 
\item Close the lid gently.
\item Centrifuge for 1 min at 8000 x g to elute the RNA.
\comment{I repeated the elution of the RNA with an extra 30~\uL of RNase-free water, which makes a final volume of 80~\uL of RNase-free water containing the RNA.}
\end{enumerate}

\subsubsection{Genomic DNA purification}

\begin{enumerate}
\item Add 500~\uL of Buffer AW1 to the AllPrep\cR DNA spin column from the Lysis.
\mistake{I accidentaly added the AW2 buffer instead of AW2, so I just centrifuged for 15 sec., discarded flow-through, and then added the 500\uL of Buffer AW1 in the AllPrep\cR DNA spin column and I proceeded with the following steps as described.}
\item Close the lid.
\item Centrifuge for 15 sec. at 8000 x g at 4\degree C to wash the column membrane.
\item Discard the flow-thought.
\item Add 500~\uL of Buffer AW2 to the AllPrep\cR DNA spin column
\item Centrifuge for 2 min at maximum speed (20 000 x g) at 4\degree C to wash the column membrane.
\item Place the AllPrep\cR DNA spin column in a new 1.5~mL collection tube.
\item Add 100~\uL of Tris-HCl buffer (pH 8) to the DNA AllPrep\cR spin column membrane and close the lid.
\item Incubate at room temperature for 1 min.
\item Centrifuge for 1 min at 8000 x g to elute the DNA.
\mistake{I forgot to incubate for one minute the first time! lucky I actually repeat this step.}
\comment{I did not repeat the elution with an extra 100\uL, so my final volume is 100\uL.}
\end{enumerate}
