% mainfile: ../../../../master.tex
\subsection{Ph.D. progress meeting}
% The part of the label after the colon must match the file name. Otherwise,
% conditional compilation based on task labels does NOT work.
\label{task:20180221_cj0}
\tags{meet,phd}
\authors{cj}
%\files{}
\persons{Viggó Þór Marteinsson}

Before the meeting, I spent some time (about two hours) preparing the presentation and putting all together my results.

\subsubsection{Work carried out since last meeting}
% Here you can write what you have been doing since the last supervisor meeting

\sidenote{\url{https://www.qiagen.com/us/shop/sample-technologies/combined-sample-technologies/allprep-dnarna-micro-kit}}
\sidenote{\url{http://www.lucigen.com/MasterPure-Complete-DNA-and-RNA-Purification-Kit/}}
\begin{itemize}
    \item[-] simultaneous purification of DNA and RNA from micro-algae cultures with AllPrep DNA/RNA Micro Kit by QIAGEN
    \item[-] subsequent isolation of DNA and RNA from micro-algae cultures with MasterPure\texttrademark~ Complete DNA and RNA Purification Kit by epicentre
    \item[-] quantification of nucleic acid yields
    \item[-] comparison of nucleic acid yields
    \item[-] reverse-transcription of extracted RNA
    \item[-] amplification by PCR of DNA and cDNA samples
    \item[-] assesment of DNA quality on 1\% agarose gel
\end{itemize}

\subsubsection{Needed input}
% Here you can write which input you need and what you would like to discuss
\begin{itemize}
    \item[-] AllPrep of MasterPure\texttrademark for metagenomic and metatranscriptomics?
    \comment{We concluded that I should try the AllPrep method with a bead beating step and run the DNA on the gel to see how it compare. Much shearing of the DNA because of the bead beating?
Viggó gave me his approval to order a AllPrep kit, but I will have to test this new kit before working on my samples.}
	\item[-] HiSeq sequencing?
	\comment{I should contact another company in Canada for the HiSeq}
	\item[-] Prioritising metagenomes over SIP ?
	\comment{yes! And it is ok for me to focus on the metagenomic project for now, and I will focus on SIP after I send my samples for sequencing.}
	\item[-] Diversity based on metagenomes x FCM?
	\comment{Good idea!}
\end{itemize}

\subsubsection{Follow-up on the meeting}
% Here you can write something about which actions must be taken based on the meeting
\begin{itemize}
    \item[-] Bead beating + AllPrep
    \item[-] Contact McGill University and Génome Québec Innovation Centre \sidenote{\url{http://gqinnovationcenter.com/services/sequencing/technoMPSIlluminaHiSeq.aspx?l=e}}
    \item[-] Order a new AllPrep kit.
\end{itemize}
